A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2018-09-29 paper/prab.tex
clarify OPAL integration

  \caption{Schematic view of messages passed within the network between the
    three roles.
  The dashed cyan path describes a request (job $j_1$) sent from $O_i$ to the
  \textsc{Pilot} being handled by $W_j$. Subsequently the result $r_k$ is
  returned to the requesting \textsc{Optimizer} ($O_i$).}
  \label{fig:opt-framework-layout}
\end{figure}

@@

In most cases \textsc{Simulation} implementations are simple wrappers to run
  an existing ``external'' simulation code using a set of design variables as
  input.
As for the \textsc{Optimizer} component there exists a base class, labeled
  \texttt{Simulation} as common basis for all \textsc{Simulation}
  implementations.
In addition, this component also inherits from the \texttt{Worker} class,
  already implementing the polling protocol for default worker types.
As shown in the API in Listing 3 the \texttt{Worker} class expects an
  implementation to provide implementations for those three methods.

>>>>

  \caption{Schematic view of messages passed within the network between the
    three roles.
  The dashed cyan path describes a request (job $j_1$) sent from $O_i$ to the
  \textsc{Pilot} being handled by $W_j$. Subsequently the result $r_k$ is
  returned to the requesting \textsc{Optimizer} ($O_i$). The work $W_j$ are beam dynamics 
  simulation within OPAL.}
  \label{fig:opt-framework-layout}
\end{figure}

@@

In most cases forward solver implementations are simple wrappers to run
  an existing ``external'' simulation code using a set of design variables as
  input. In case of the OPAL integration, basically the \texttt{main} function is
  playing the role of the ``forward solver''. Underlying the general nature of our approach, 
  in a similar project, we use the described methods for cavity shape optimisation based on \cite{ARBENZ2008381}. 
As for the \textsc{Optimizer} component there exists a base class, labeled
  \texttt{Simulation} as common basis for all \textsc{Simulation}
  implementations.
In addition, this component also inherits from the \texttt{Worker} class,
  already implementing the polling protocol for default worker types.
As shown in the API in Listing 3 the \texttt{Worker} class expects an
  implementation to provide implementations for those three methods.
